*Supplement* Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-10-26 manu-draft.qmd
add supplement gam fit stats

```{r}
#| results: hide
library(knitr)
library(here)
library(flextable)

load(file = here('tabs/mixdaytab.RData'))
```

@@

@@

Because of the uncertainty in defining thresholds for optimal temperature and salinity ranges, multiple thresholds were evaluated to both describe the potential for stress and how it may be related to changes in seagrass. Distinctions were not made between species, primarily due to lack of consensus between studies and the likely site-specific ranges that affect seagrass growth in Tampa Bay. First, we developed metrics of potential temperature and salinity stress by quantifying the maximum number of continuous days each year when temperature was above or salinity was below a given threshold. This approach assumed that stress could be observed based on duration of exposure (i.e., maximum number of continuous days each year) relative to a threshold that may are may not be outside of the optimum range for seagrasses. These metrics were quantified from the monthly long-term observation in the EPC data. To quantify daily counts each year, a continuous prediction of temperature or stress over time was estimated using Generalized Additive Models (GAMs) fit to the response variable and a single predictor for decimal year. The smoothing spline for decimal year had sufficient knots to capture the seasonal signal within each year and the long-term inter-annual trends [@beck2022a]. Model fit for each station was sufficient to calculate daily predictions for assessing the stressor metrics.

>>>>

```{r}
#| results: hide
library(knitr)
library(here)
library(flextable)
library(dplyr)
library(tibble)

load(file = here('data/gamfit.RData'))
load(file = here('tabs/mixdaytab.RData'))
```

@@

```{r}
# r2 range for gam daily  models
fitest <- gamfit %>% 
  summarise(
    minr2 = min(R2), 
    maxr2 = max(R2), 
    .by = parameter
  ) %>% 
  split(.$parameter)
```

@@

Because of the uncertainty in defining thresholds for optimal temperature and salinity ranges, multiple thresholds were evaluated to both describe the potential for stress and how it may be related to changes in seagrass. Distinctions were not made between species, primarily due to lack of consensus between studies and the likely site-specific ranges that affect seagrass growth in Tampa Bay. First, we developed metrics of potential temperature and salinity stress by quantifying the maximum number of continuous days each year when temperature was above or salinity was below a given threshold. This approach assumed that stress could be observed based on duration of exposure (i.e., maximum number of continuous days each year) relative to a threshold that may are may not be outside of the optimum range for seagrasses. These metrics were quantified from the monthly long-term observation in the EPC data. To quantify daily counts each year, a continuous prediction of temperature or stress over time was estimated using Generalized Additive Models (GAMs) fit to the response variable and a single predictor for decimal year. The smoothing spline for decimal year had sufficient knots to capture the seasonal signal within each year and the long-term inter-annual trends [@beck2022a]. Model fit for each station was sufficient to calculate daily predictions for assessing the stressor metrics (see supplement, R$^2$ ranged from `r fitest$temp$minr2` to `r fitest$temp$maxr2` for temperature models, `r fitest$sal$minr2` to `r fitest$sal$maxr2` for salinity models).

### 2023-10-26 supplement.qmd
add supplement gam fit stats

load(file = here('tabs/supp1mixtab.RData'))
load(file = here('tabs/supp2mixtab.RData'))
load(file = here('tabs/supp1daytab.RData'))
load(file = here('tabs/supp2daytab.RData'))
```

@@

>>>>

load(file = here('tabs/supptempfittab.RData'))
load(file = here('tabs/suppsalifittab.RData'))
load(file = here('tabs/supp1mixtab.RData'))
load(file = here('tabs/supp2mixtab.RData'))
load(file = here('tabs/supp1daytab.RData'))
load(file = here('tabs/supp2daytab.RData'))
```

@@

```{r}
#| tbl-cap: "Summary statistics for Generalized Additive Model fits to bottom water temperature data at all stations in Tampa Bay monitored by the Environmental Protection Commission of Hillsborough County. Models were fit on monthly data from 1975 to 2022 using decimal year as the single predictor. Fit statistics are Akaike Information Criterion (AIC), Generalized Cross-Validation (GCV) scores, and R-squared values of observed to predicted. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay."
#| label: tbl-supptempfittab
supptempfittab
```

```{r}
#| tbl-cap: "Summary statistics for Generalized Additive Model fits to bottom salinity data at all stations in Tampa Bay monitored by the Environmental Protection Commission of Hillsborough County. Models were fit on monthly data from 1975 to 2022 using decimal year as the single predictor. Fit statistics are Akaike Information Criterion (AIC), Generalized Cross-Validation (GCV) scores, and R-squared values of observed to predicted. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay."
#| label: tbl-suppsalifittab
suppsalifittab
```
